Chord: A Versatile Platform for Program Analysis

### 2011-03-14 main/doc/properties.tex
new documentation

% TODO: write some text at beginning of each subsection
% TODO: do cross-referencing (i.e. put "See Also" for properties used by multiple subsections)

\section{Chord System Properties}
\label{sec:chord-sysprops}

Users can use system properties to control Chord's execution.
The following properties are recognized by Chord.
The separator for list-valued properties can be either a blank space, a comma, a colon, or a semi-colon.
Notation {\tt [<...>]} is used in this section to denote the value of the property named {\tt <...>}.

\paragraph{Program Properties}

This section describes basic properties of the given program, such as
its main class, the location(s) of its class files and Java source
files, and command-line arguments to be used to run the program.

\noindent \code{chord.work.dir}
\begin{quote}
{\bf Type:} location \\
{\bf Description:} Working directory during Chord's execution.  This is
usually the top-level directory of the given program. \\
{\bf Default value:} current working directory
\end{quote}

\noindent \code{chord.props.file}
\begin{quote}
{\bf Type:} location \\
{\bf Description:} Properties file loaded by Chord at the
beginning before doing anything else.  Any of the below properties may
be defined in this file to avoid defining them on the command line
(using the \code{-D<key>=<value>} format) every time Chord is run.
Each relative file/directory name in the value of any property defined
in this file is treated relative to Chord's working directory (which
is specified by property \code{chord.work.dir}). \\
{\bf Default value:} \code{[chord.work.dir]/chord.properties}
\end{quote}

\noindent \code{chord.main.class}
\begin{quote}
{\bf Type:} class \\
{\bf Description:} Fully-qualified name of the main class of the given program (e.g., \code{com.example.Main}).
\end{quote}

\noindent \code{chord.class.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} Classpath of the given program.  It does not need to include
boot classes (i.e., classes in \code{[sun.boot.class.path]}) or
standard extensions (i.e., classes in {\tt .jar} files in directory
\code{[java.home]/lib/ext/}). \\
{\bf Default value:} {\tt ""}
\end{quote}

\noindent \code{chord.src.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} Java source path of the given program. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} Chord analyzes only Java bytecode, not Java source code.  This property is used only by the task of converting Java source files into HTML files by program analyses that need to present their analysis results at the Java source code level (by calling method \code{chord.program.Program.g().HTMLizeJavaSrcFiles())}.
\end{quote}

\noindent \code{chord.run.ids}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} List of IDs to identify runs of the given program. \\
{\bf Default value:} {\tt 0} \\
{\bf Note:} This property is used only when Chord executes the given program, namely, when it is asked to compute the program scope dynamically (i.e., when \code{[chord.scope.kind]=dynamic}) or when it is asked to execute a dynamic program analysis. 
\end{quote}

\noindent \code{chord.args.<id>}
\begin{quote}
{\bf Type:} string \\
{\bf Description:} Command-line arguments string to be used for the given program in the run having ID {\tt <id>}. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} This property is used only when Chord executes the given program, namely, when it is asked to compute the program scope dynamically (i.e., when \code{[chord.scope.kind]=dynamic}) or when it is asked to execute a dynamic program analysis.
\end{quote}

\noindent \code{chord.runtime.jvmargs}
\begin{quote}
{\bf Type:} string \\
{\bf Description:} Arguments to JVM which runs the given program. \\
{\bf Default value:} {\tt "-ea -Xmx1024m"} \\
{\bf Note:} This property is used only when Chord executes the given program, namely, when it is asked to compute the program scope dynamically (i.e., when \code{[chord.scope.kind]=dynamic}) or when it is asked to execute a dynamic program analysis. 
\end{quote}

\paragraph{Analysis Scope Properties}

This section describes properties that specify how the analysis scope of the given program is computed.
See Section \ref{sec:building-scope} for more details.

\noindent \code{chord.scope.kind}
\begin{quote}
{\bf Type:} {\tt [dynamic|rta|cha]} \\
{\bf Description:} Algorithm to compute program scope.  The choices are {\tt dynamic} (dynamic analysis), {\tt rta} (Rapid Type Analysis), and {\tt cha} (Class Hierarchy Analysis). \\
{\bf Default value:} {\tt rta}
\end{quote}

\noindent \code{chord.reflect.kind}
\begin{quote}
{\bf Type:} {\tt [none|static|dynamic|static_cast]} \\
{\bf Description:} TODO \\
{\bf Default value:} {\tt none}
\end{quote}

\noindent \code{chord.ch.kind}
\begin{quote}
{\bf Type:} {\tt [static|dynamic]} \\
{\bf Description:} Algorithm to build the class hierarchy.  If it is {\tt dynamic}, then the given program is executed and classes not loaded by the JVM while running the program are excluded while building the class hierarchy. \\
{\bf Default value:} {\tt static} \\
{\bf Note:} This property is relevant only if \code{chord.scope.kind} is {\tt cha} since only this scope computing algorithm queries the class hierarchy. 
\end{quote}

\noindent \code{chord.ssa}
\begin{quote}
{\bf Type:} bool  \\
{\bf Description:} Do SSA transformation for all methods deemed reachable by the algorithm used to compute program scope. \\
{\bf Default value:} {\tt true}
\end{quote}

@@

\noindent \code{chord.std.scope.exclude}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} Partial list of prefixes of names of classes whose declared methods must be treated as no-ops.  Conventionally, this property is used to specify classes to be excluded from the scope of all programs to be analyzed, e.g., classes in the JDK standard library. \\
{\bf Default value:} {\tt ""}
\end{quote}

\noindent \code{chord.ext.scope.exclude}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} Partial list of prefixes of names of classes whose declared methods must be treated as no-ops.  Conventionally, this property is used to specify classes to be excluded from the scope of specific programs to be analyzed. \\
{\bf Default value:} {\tt ""}
\end{quote}

\noindent \code{chord.scope.exclude}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} Complete list of prefixes of names of classes whose declared methods must be treated as no-ops. \\
{\bf Default value:} \code{"[chord.std.scope.exclude],[chord.ext.scope.exclude]"}
\end{quote}

\noindent \code{chord.std.check.exclude}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes and packages inside the standard library to be excluded by program analyses.  Interpretation of this property is analysis-specific. \\
{\bf Default value:} \code{"java.,javax.,sun.,com.sun.,com.ibm.,} \code{org.apache.harmony."}
\end{quote}

\noindent \code{chord.ext.check.exclude}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes and packages outside the standard library to be excluded by program analyses.  Interpretation of this property is analysis-specific. \\
{\bf Default value:} {\tt ""}
\end{quote}

\noindent \code{chord.check.exclude}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes and packages to be excluded by program analyses.  Interpretation of this property is analysis-specific. \\
{\bf Default value:} \code{"[chord.std.check.exclude],[chord.ext.check.exclude]"}
\end{quote}

\paragraph{Functionality Properties}

This section describes properties that dictate what Chord outputs during execution.

\noindent \code{chord.build.scope}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Compute the scope of the given program using the algorithm specified by properties \code{chord.scope.kind} and \code{chord.reuse.scope}. \\
{\bf Default value:} {\tt false} \\
{\bf Note:} The program scope is computed regardless of the value of this property if another task (e.g., a program analysis specified via property \code{chord.run.analyses}) demands it by calling method \code{chord.program.Program.g()}. 
\end{quote}

\noindent \code{chord.run.analyses}
\begin{quote}
{\bf Type:} string list  \\
{\bf Description:} List of names of program analyses to be run in order. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} If the analysis is written in Java, its name is specified via statement {\tt name=<...>} in its {\tt @Chord} annotation, and is the name of the class itself if this statement is missing.  If the analysis is written in Datalog, its name is specified via a line of the form ``{\tt \# name=<...>}", and is the absolute location of the file itself if this line is missing. 
\end{quote}

\noindent \code{chord.print.methods}
\begin{quote}
{\bf Type:} string list  \\
{\bf Description:} List of methods in scope whose intermediate representation to print to standard output. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} Specify each method in format \code{<mname>:<mdesc>@<cname>} where {\tt <mname>} is the method's name, {\tt <mdesc>} is the method's descriptor, and {\tt <cname>} is the name of the method's declaring class. In {\tt <cname>}, use `.' instead of `/', and use {\tt \#} instead of the dollar character. 
\end{quote}

\noindent \code{chord.print.classes}
\begin{quote}
{\bf Type:} string list  \\
{\bf Description:} List of classes in scope whose intermediate representation to print to standard output. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} In class names, use `.' instead of `/', and use {\tt \#} instead of the dollar character. 
\end{quote}

\noindent \code{chord.print.all.classes}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Print intermediate representation of all classes in scope to standard output. \\
{\bf Default value:} {\tt false}
\end{quote}

\noindent \code{chord.print.rels}
\begin{quote}
{\bf Type:} string list  \\
{\bf Description:} List of names of program relations whose contents must be printed to files \code{[chord.out.dir]/<...>.txt} where {\tt <...>} denotes the relation name. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} This functionality must be used with caution as certain program relations, albeit represented compactly as BDDs, may contain a large number (e.g., billions) of tuples, resulting in voluminous output when printed to a file.  See Section \ref{sec:tuning-datalog-analysis} for a more efficient way to query the contents of program relations (namely, by using the {\tt debug} target provided in file {\tt build.xml} in Chord's {\tt main/} directory). 
\end{quote}

\noindent \code{chord.print.project}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Create files \code{targets_sortby_name.html}, \code{targets_sortby_kind.html}, and \code{targets_sortby_producers.html} in directory \code{[chord.out.dir]}, publishing all tasks and targets defined by program analyses in paths \code{[chord.java.analysis.path]} and \code{[chord.dlog.analysis.path]}.  \\
{\bf Default value:} {\tt false}
\end{quote}

\noindent \code{chord.print.results}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Print the results of program analyses in HTML.  Interpretation of this property is analysis-specific.  \\
{\bf Default value:} {\tt true}
\end{quote}

\noindent \code{chord.verbose}
\begin{quote}
{\bf Type:} int in the range [0..6]  \\
{\bf Description:} Control the verbosity of logging during Chord's execution.  \\
{\bf Default value:} {\tt 2}
\end{quote}

\paragraph{Project Properties}

This section describes properties regarding program analyses executed by Chord.

\noindent \code{chord.classic}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} TODO \\
{\bf Default value:} TODO
\end{quote}

\noindent \code{chord.std.java.analysis.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} TODO \\
{\bf Default value:} TODO
\end{quote}

\noindent \code{chord.ext.java.analysis.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} TODO \\
{\bf Default value:} TODO
\end{quote}

\noindent \code{chord.java.analysis.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} Classpath containing program analyses written in Java (i.e., {\tt @Chord}-annotated classes).  \\
{\bf Default value:} \code{[chord.main.dir]/classes/}
\end{quote}

\noindent \code{chord.std.dlog.analysis.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} TODO \\
{\bf Default value:} TODO
\end{quote}

\noindent \code{chord.ext.dlog.analysis.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} TODO \\
{\bf Default value:} TODO
\end{quote}

\noindent \code{chord.dlog.analysis.path}
\begin{quote}
{\bf Type:} path  \\
{\bf Description:} Path of directories containing program analyses written in Datalog (i.e., files with suffix {\tt .dlog} or {\tt .datalog}). \\
{\bf Default value:} \code{[chord.main.dir]/src/}
\end{quote}

\paragraph{Instrumentation Properties}

This section describes properties regarding execution of instrumented programs for dynamic analyses.

% TODO: mention chord.scope.exclude* here
\noindent \code{chord.use.jvmti}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} TODO \\
{\bf Default value:} TODO
\end{quote}

\noindent \code{chord.instr.kind}
\begin{quote}
{\bf Type:} {\tt [offline|online]}  \\
{\bf Description:} The kind of bytecode instrumentation.  The choices are offline and online (load-time).  \\
{\bf Default value:} {\tt offline}
\end{quote}

\noindent \code{chord.trace.kind}
\begin{quote}
{\bf Type:} {\tt [full|pipe]}  \\
{\bf Description:} The medium by which an event-generating JVM and an event-handling JVM communicate in a dynamic analysis.  The choices are regular file and POSIX pipe.  \\
{\bf Default value:} {\tt full} 
\end{quote}

\noindent \code{chord.trace.block.size}
\begin{quote}
{\bf Type:} int \\
{\bf Description:} Number of bytes to read/write in a single operation from/to the event file used by a multi-JVM dynamic analysis. \\
{\bf Default value:} {\tt 4096}
\end{quote}

\noindent \code{chord.dynamic.haltonerr}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Whether or not to terminate Chord if the given program terminates abnormally during dynamic analysis. \\
{\bf Default value:} true
\end{quote}

\noindent \code{chord.dynamic.timeout}
\begin{quote}
{\bf Type:} int  \\
{\bf Description:} The amount of time, in milliseconds, after which to kill the process running the given program during dynamic analysis, or -1 if the process must never be killed. \\
{\bf Default value:} {\tt -1}
\end{quote}

\noindent \code{chord.max.cons.size}
\begin{quote}
{\bf Type:} int \\
{\bf Description:} Maximum number of bytes over which events generated during the execution of any constructor in the given program may span. \\
{\bf Default value:} {\tt 50000000} \\
{\bf Note:} This property is relevant only for dynamic analyses which want events of the form {\tt BEF\_NEW} $h$ $t$ $o$ to be generated (see Section \ref{sec:instr-events}).  The problem with generating such events at run-time is that the ID $o$ of the object freshly created by thread $t$ at object allocation site $h$ cannot be instrumented until the object is fully initialized (i.e., its constructor has finished executing).  Hence, Chord first generates a ``crude dynamic trace", which has events of the form {\tt BEF\_NEW} $h$ $t$ and {\tt AFT\_NEW} $h$ $t$ $o$ generated before and after the execution of the constructor, respectively.  A subsequent pass generates a ``final dynamic trace", which replaces each {\tt BEF\_NEW} $h$ $t$ event by {\tt BEF\_NEW} $h$ $t$ $o$.  For this purpose, however, Chord must buffer all events generated between the {\tt BEF\_NEW} and {\tt AFT\_NEW} events, and this property specifies the number of bytes over which these events may span.  If the actual number of bytes exceeds the value specified by this property (e.g., if the constructor throws an exception and the {\tt AFT\_NEW} event is not generated at all), then Chord simply generates event {\tt BEF\_NEW} $h$ $i$ $0$ (i.e., it treats the created object as having ID 0, which is the ID also used for {\tt null}). 
\end{quote}

\paragraph{Caching Properties}

TODO

\noindent \code{chord.reuse.scope}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Compute program scope using the information in files specified by properties \code{chord.methods.file} and \code{chord.reflect.file}. \\
{\bf Default value:} {\tt false} \\
{\bf Note:} Property \code{chord.scope.kind} is ignored if this property is set to {\tt true} and the two files exist. 
\end{quote}

\noindent \code{chord.reuse.rels}
\begin{quote}
{\bf Type:} bool  \\
{\bf Description:} Construct program relations from BDDs stored on disk (from a previous run of Chord) whenever possible instead of re-computing them. \\
{\bf Default value:} {\tt false}
\end{quote}

\noindent \code{chord.reuse.traces}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Reuse dynamic traces computed by a previous run of Chord if they exist.  Property \code{chord.trace.kind} must be set to {\tt full} if this property is set to {\tt true}. \\
{\bf Default value:} {\tt false}
\end{quote}

\paragraph{Chord JVM Properties}

TODO

>>>>

\chapter{Chord Properties}
\label{chap:properties}

The only way to specify inputs to Chord is by means of system properties.
There is no command-line argument processing in Chord and any command-line arguments are ignored.
Section \ref{sec:properties-setting} explains how to set properties and
Section \ref{sec:properties-meaning} explains the meaning of properties recognized by Chord.

\section{How to Set Properties}
\label{sec:properties-setting}

A property can be passed to Chord in any of several ways.
The reason for providing multiple ways is to provide users shorthand ways for defining properties
once and for all for a particular input Java program, or even once and for all across all Chord runs. 
The following are the different ways by which a property can be passed to Chord in decreasing order of precedence:
\begin{enumerate}
\item
On the command-line via the \code{-D<key>=<value>} format.

Use this option to specify properties specific to the current run of Chord.

Typical usage of this option is by running the following command in
the \code{main/} directory of Chord's installation:
\begin{verbatim}
    prompt> ant -D<key1>=<value1> ... -D<keyN>=<valueN> run
\end{verbatim}

\item
Via the file specified by property \code{chord.props.file}.

Use this option to specify once and for all properties of the program to
be analyzed (e.g., property \code{chord.main.class} specifying the name of that program's main class, property \code{chord.class.path}
specifying the application classpath of that program, etc.).

The default value of this property is \code{[chord.work.dir]/chord.properties} and typically
does not need to be changed by users.
Property \code{chord.work.dir} specifies the directory in which Chord will run.
The default value of this property is the current directory but users must typically set
it on the command line, as follows:

\begin{verbatim}
    prompt> ant -Dchord.work.dir=<...> run
\end{verbatim}
where ``\code{<...>}" denotes the absolute or relative path of the top-level directory of
the program to be analyzed, which contains a file named \code{chord.properties} that users
must create themselves and populate with properties that are recognized by chord and
are specific to that program.

\item
Via file \code{main/chord.properties}.

Use this option to specify once and for all properties you would like to hold in every run of Chord
(e.g., property \code{chord.max.heap} specifying the maximum runtime heap size to be used by the
JVM running Chord).
\end{enumerate}

\section{Meaning of Properties}
\label{sec:properties-meaning}

The following properties are recognized by Chord.
The separator for list-valued properties can be either a blank space, a comma, a colon, or a semi-colon.
Notation {\tt [<...>]} is used in this section to denote the value of the property named {\tt <...>}.

\subsection{Java Program Properties} 
\label{sec:program-props}

This section describes basic properties of the given Java program, such as
its main class, the location(s) of its class files and Java source
files, and command-line arguments to be used to run the program.
\\[10pt]

\code{chord.work.dir}
\begin{quote}
{\bf Type:} location \\
{\bf Description:} Working directory during Chord's execution.  This is
usually the top-level directory of the given program. \\
{\bf Default value:} current working directory
\end{quote}

\code{chord.props.file}
\begin{quote}
{\bf Type:} location \\
{\bf Description:} Properties file loaded by Chord at the
beginning before doing anything else.  Any of the below properties may
be defined in this file to avoid defining them on the command line
(using the \code{-D<key>=<value>} format) every time Chord is run.
Each relative file/directory name in the value of any property defined
in this file is treated relative to Chord's working directory (which
is specified by property \code{chord.work.dir}). \\
{\bf Default value:} \code{[chord.work.dir]/chord.properties}
\end{quote}

\code{chord.main.class}
\begin{quote}
{\bf Type:} class \\
{\bf Description:} Fully-qualified name of the main class of the given program (e.g., \code{com.example.Main}).
\end{quote}

\code{chord.class.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} Classpath of the given program.  It does not need to include
boot classes (i.e., classes in \code{[sun.boot.class.path]}) or
standard extensions (i.e., classes in {\tt .jar} files in directory
\code{[java.home]/lib/ext/}). \\
{\bf Default value:} {\tt ""}
\end{quote}

\code{chord.src.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} Java source path of the given program. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} Chord analyzes only Java bytecode, not Java source code.  This property is used only by the task of converting Java source files into HTML files by program analyses that need to present their analysis results at the Java source code level (by calling method \code{chord.program.Program.g().HTMLizeJavaSrcFiles())}.
\end{quote}

\code{chord.run.ids}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} List of IDs to identify runs of the given program. \\
{\bf Default value:} {\tt 0} \\
{\bf Note:} This property is used only when Chord executes the given program, namely, when it is asked to compute the program scope dynamically (i.e., when \code{[chord.scope.kind]=dynamic}) or when it is asked to execute a dynamic program analysis. 
\end{quote}

\code{chord.args.<id>}
\begin{quote}
{\bf Type:} string \\
{\bf Description:} Command-line arguments string to be used for the given program in the run having ID {\tt <id>}. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} This property is used only when Chord executes the given program, namely, when it is asked to compute the program scope dynamically (i.e., when \code{[chord.scope.kind]=dynamic}) or when it is asked to execute a dynamic program analysis.
\end{quote}

\code{chord.runtime.jvmargs}
\begin{quote}
{\bf Type:} string \\
{\bf Description:} Arguments to JVM which runs the given program. \\
{\bf Default value:} {\tt "-ea -Xmx1024m"} \\
{\bf Note:} This property is used only when Chord executes the given program, namely, when it is asked to compute the program scope dynamically (i.e., when \code{[chord.scope.kind]=dynamic}) or when it is asked to execute a dynamic program analysis. 
\end{quote}

\subsection{Analysis Scope Properties}
\label{sec:scope-props}

This section describes properties that specify how the analysis scope of the given program is computed.
See Chapter \ref{chap:computing-scope} for more details.
\\[10pt]

\code{chord.scope.kind}
\begin{quote}
{\bf Type:} {\tt [dynamic|rta|cha]} \\
{\bf Description:} Algorithm to compute program scope.  The choices are {\tt dynamic} (dynamic analysis), {\tt rta} (Rapid Type Analysis), and {\tt cha} (Class Hierarchy Analysis). \\
{\bf Default value:} {\tt rta}
\end{quote}

\code{chord.reflect.kind}
\begin{quote}
{\bf Type:} {\tt [none|static|dynamic|static\_cast]} \\
{\bf Description:} TODO \\
{\bf Default value:} {\tt none}
\end{quote}

\code{chord.ch.kind}
\begin{quote}
{\bf Type:} {\tt [static|dynamic]} \\
{\bf Description:} Algorithm to build the class hierarchy.  If it is {\tt dynamic}, then the given program is executed and classes not loaded by the JVM while running the program are excluded while building the class hierarchy. \\
{\bf Default value:} {\tt static} \\
{\bf Note:} This property is relevant only if \code{chord.scope.kind} is {\tt cha} since only this scope computing algorithm queries the class hierarchy. 
\end{quote}

\code{chord.ssa}
\begin{quote}
{\bf Type:} bool  \\
{\bf Description:} Do SSA transformation for all methods deemed reachable by the algorithm used to compute program scope. \\
{\bf Default value:} {\tt true}
\end{quote}

@@

\code{chord.std.scope.exclude}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} Partial list of prefixes of names of classes whose declared methods must be treated as no-ops.  Conventionally, this property is used to specify classes to be excluded from the scope of all programs to be analyzed, e.g., classes in the JDK standard library. \\
{\bf Default value:} {\tt ""}
\end{quote}

\code{chord.ext.scope.exclude}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} Partial list of prefixes of names of classes whose declared methods must be treated as no-ops.  Conventionally, this property is used to specify classes to be excluded from the scope of specific programs to be analyzed. \\
{\bf Default value:} {\tt ""}
\end{quote}

\code{chord.scope.exclude}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} Complete list of prefixes of names of classes whose declared methods must be treated as no-ops. \\
{\bf Default value:} \code{"[chord.std.scope.exclude],[chord.ext.scope.exclude]"}
\end{quote}

\code{chord.std.check.exclude}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes and packages inside the standard library to be excluded by program analyses.  Interpretation of this property is analysis-specific. \\
{\bf Default value:} \code{"java.,javax.,sun.,com.sun.,com.ibm.,} \code{org.apache.harmony."}
\end{quote}

\code{chord.ext.check.exclude}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes and packages outside the standard library to be excluded by program analyses.  Interpretation of this property is analysis-specific. \\
{\bf Default value:} {\tt ""}
\end{quote}

\code{chord.check.exclude}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes and packages to be excluded by program analyses.  Interpretation of this property is analysis-specific. \\
{\bf Default value:} \code{"[chord.std.check.exclude],[chord.ext.check.exclude]"}
\end{quote}

\subsection{Functionality Properties}
\label{sec:func-props}

This section describes properties that dictate what task(s) Chord must perform.
\\[10pt]

\code{chord.build.scope}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Compute the scope of the given program using the algorithm specified by properties \code{chord.scope.kind} and \code{chord.reuse.scope}. \\
{\bf Default value:} {\tt false} \\
{\bf Note:} The program scope is computed regardless of the value of this property if another task (e.g., a program analysis specified via property \code{chord.run.analyses}) demands it by calling method \code{chord.program.Program.g()}. 
\end{quote}

\code{chord.run.analyses}
\begin{quote}
{\bf Type:} string list  \\
{\bf Description:} List of names of program analyses to be run in order. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} If the analysis is written in Java, its name is specified via statement {\tt name=<...>} in its {\tt @Chord} annotation, and is the name of the class itself if this statement is missing.  If the analysis is written in Datalog, its name is specified via a line of the form ``{\tt \# name=<...>}", and is the absolute location of the file itself if this line is missing. 
\end{quote}

\code{chord.print.methods}
\begin{quote}
{\bf Type:} string list  \\
{\bf Description:} List of methods in scope whose intermediate representation to print to standard output. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} Specify each method in format \code{<mname>:<mdesc>@<cname>} where {\tt <mname>} is the method's name, {\tt <mdesc>} is the method's descriptor, and {\tt <cname>} is the name of the method's declaring class. In {\tt <cname>}, use `.' instead of `/', and use {\tt \#} instead of the dollar character. 
\end{quote}

\code{chord.print.classes}
\begin{quote}
{\bf Type:} string list  \\
{\bf Description:} List of classes in scope whose intermediate representation to print to standard output. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} In class names, use `.' instead of `/', and use {\tt \#} instead of the dollar character. 
\end{quote}

\code{chord.print.all.classes}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Print intermediate representation of all classes in scope to standard output. \\
{\bf Default value:} {\tt false}
\end{quote}

\code{chord.print.rels}
\begin{quote}
{\bf Type:} string list  \\
{\bf Description:} List of names of program relations whose contents must be printed to files \code{[chord.out.dir]/<...>.txt} where {\tt <...>} denotes the relation name. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} This functionality must be used with caution as certain program relations, albeit represented compactly as BDDs, may contain a large number (e.g., billions) of tuples, resulting in voluminous output when printed to a file.  See Section \ref{sec:tuning-datalog-analysis} for a more efficient way to query the contents of program relations (namely, by using the {\tt debug} target provided in file {\tt build.xml} in Chord's {\tt main/} directory). 
\end{quote}

\code{chord.print.project}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Create files \code{targets_sortby_name.html}, \code{targets_sortby_kind.html}, and \code{targets_sortby_producers.html} in directory \code{[chord.out.dir]}, publishing all tasks and targets defined by program analyses in paths \code{[chord.java.analysis.path]} and \code{[chord.dlog.analysis.path]}.  \\
{\bf Default value:} {\tt false}
\end{quote}

\code{chord.print.results}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Print the results of program analyses in HTML.  Interpretation of this property is analysis-specific.  \\
{\bf Default value:} {\tt true}
\end{quote}

\code{chord.verbose}
\begin{quote}
{\bf Type:} int in the range [0..6]  \\
{\bf Description:} Control the verbosity of logging during Chord's execution.  \\
{\bf Default value:} {\tt 2}
\end{quote}

\subsection{Project Properties}
\label{sec:project-props}

This section describes properties regarding program analyses executed by Chord.
\\[10pt]

\code{chord.classic}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} TODO \\
{\bf Default value:} TODO
\end{quote}

\code{chord.std.java.analysis.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} TODO \\
{\bf Default value:} TODO
\end{quote}

\code{chord.ext.java.analysis.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} TODO \\
{\bf Default value:} TODO
\end{quote}

\code{chord.java.analysis.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} Classpath containing program analyses written in Java (i.e., {\tt @Chord}-annotated classes).  \\
{\bf Default value:} \code{[chord.main.dir]/classes/}
\end{quote}

\code{chord.std.dlog.analysis.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} TODO \\
{\bf Default value:} TODO
\end{quote}

\code{chord.ext.dlog.analysis.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} TODO \\
{\bf Default value:} TODO
\end{quote}

\code{chord.dlog.analysis.path}
\begin{quote}
{\bf Type:} path  \\
{\bf Description:} Path of directories containing program analyses written in Datalog (i.e., files with suffix {\tt .dlog} or {\tt .datalog}). \\
{\bf Default value:} \code{[chord.main.dir]/src/}
\end{quote}

\subsection{Instrumentation Properties}
\label{sec:instr-props}

This section describes properties regarding execution of instrumented programs for dynamic analyses.
\\[10pt]

% TODO: mention chord.scope.exclude* here
\code{chord.use.jvmti}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} TODO \\
{\bf Default value:} TODO
\end{quote}

\code{chord.instr.kind}
\begin{quote}
{\bf Type:} {\tt [offline|online]}  \\
{\bf Description:} The kind of bytecode instrumentation.  The choices are offline and online (load-time).  \\
{\bf Default value:} {\tt offline}
\end{quote}

\code{chord.trace.kind}
\begin{quote}
{\bf Type:} {\tt [full|pipe]}  \\
{\bf Description:} The medium by which an event-generating JVM and an event-handling JVM communicate in a dynamic analysis.  The choices are regular file and POSIX pipe.  \\
{\bf Default value:} {\tt full} 
\end{quote}

\code{chord.trace.block.size}
\begin{quote}
{\bf Type:} int \\
{\bf Description:} Number of bytes to read/write in a single operation from/to the event file used by a multi-JVM dynamic analysis. \\
{\bf Default value:} {\tt 4096}
\end{quote}

\code{chord.dynamic.haltonerr}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Whether or not to terminate Chord if the given program terminates abnormally during dynamic analysis. \\
{\bf Default value:} true
\end{quote}

\code{chord.dynamic.timeout}
\begin{quote}
{\bf Type:} int  \\
{\bf Description:} The amount of time, in milliseconds, after which to kill the process running the given program during dynamic analysis, or -1 if the process must never be killed. \\
{\bf Default value:} {\tt -1}
\end{quote}

\code{chord.max.cons.size}
\begin{quote}
{\bf Type:} int \\
{\bf Description:} Maximum number of bytes over which events generated during the execution of any constructor in the given program may span. \\
{\bf Default value:} {\tt 50000000} \\
{\bf Note:} This property is relevant only for dynamic analyses which want events of the form {\tt BEF\_NEW} $h$ $t$ $o$ to be generated (see Section \ref{sec:instr-events}).  The problem with generating such events at run-time is that the ID $o$ of the object freshly created by thread $t$ at object allocation site $h$ cannot be instrumented until the object is fully initialized (i.e., its constructor has finished executing).  Hence, Chord first generates a ``crude dynamic trace", which has events of the form {\tt BEF\_NEW} $h$ $t$ and {\tt AFT\_NEW} $h$ $t$ $o$ generated before and after the execution of the constructor, respectively.  A subsequent pass generates a ``final dynamic trace", which replaces each {\tt BEF\_NEW} $h$ $t$ event by {\tt BEF\_NEW} $h$ $t$ $o$.  For this purpose, however, Chord must buffer all events generated between the {\tt BEF\_NEW} and {\tt AFT\_NEW} events, and this property specifies the number of bytes over which these events may span.  If the actual number of bytes exceeds the value specified by this property (e.g., if the constructor throws an exception and the {\tt AFT\_NEW} event is not generated at all), then Chord simply generates event {\tt BEF\_NEW} $h$ $i$ $0$ (i.e., it treats the created object as having ID 0, which is the ID also used for {\tt null}). 
\end{quote}

\subsection{Caching Properties}
\label{sec:caching-props}

TODO
\\[10pt]

\code{chord.reuse.scope}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Compute program scope using the information in files specified by properties \code{chord.methods.file} and \code{chord.reflect.file}. \\
{\bf Default value:} {\tt false} \\
{\bf Note:} Property \code{chord.scope.kind} is ignored if this property is set to {\tt true} and the two files exist. 
\end{quote}

\code{chord.reuse.rels}
\begin{quote}
{\bf Type:} bool  \\
{\bf Description:} Construct program relations from BDDs stored on disk (from a previous run of Chord) whenever possible instead of re-computing them. \\
{\bf Default value:} {\tt false}
\end{quote}

\code{chord.reuse.traces}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Reuse dynamic traces computed by a previous run of Chord if they exist.  Property \code{chord.trace.kind} must be set to {\tt full} if this property is set to {\tt true}. \\
{\bf Default value:} {\tt false}
\end{quote}

\subsection{Chord JVM Properties}
\label{sec:jvm-props}

TODO
\\[10pt]

\code{java.class.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} TODO \\
{\bf Default value:} TODO
\end{quote}
